Domain-agnostic Outlier Ranking Algorithms (DORA)---A Configurable Pipeline for Facilitating Outlier Detection in Scientific Datasets

### 2022-02-01 publications/frontiers/dora_outlier_detection_frontiers.tex
Add link to dataset on Zenodo.

\section*{Data Availability Statement}
The datasets [GENERATED/ANALYZED] for this study can be found in the [NAME OF REPOSITORY] [LINK]. 
% Please see the availability of data guidelines for more information, at https://www.frontiersin.org/about/author-guidelines#AvailabilityofData

>>>>

\section*{Data Availability Statement}
The datasets generated and analyzed for this study can be found in the
``Multi-Domain Outlier Detection Dataset'' repository on Zenodo 
(\url{https://doi.org/10.5281/zenodo.5941339}) (dataset will be made public
with final publication). 
% Please see the availability of data guidelines for more information, at https://www.frontiersin.org/about/author-guidelines#AvailabilityofData
